Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-24 article.rnw
Add the discussion.

>>>>

\section{Discussion}

The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}), but not confidently so.
Which grouping might give the most parsimonious model also could not be determined with any confidence.
The intransitivity of coclassification in some instances even suggests that, in some cases, there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.

This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a qualitative competitive context.
Perhaps species simply do not group to the same extent in a competitive context.
The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that speies would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.

I chose a study system of \emph{Drosophila} partially on the basis that it would allow clear analysis of the species phylogenetic relationships.
Phylogeny proved a poor predictor of optimal grouping, as previous studies have suggested that it might \parencite{godoy2014phylogenetic,cahill2008does}.
A study system with species spanning multiple functional groups, however, might have shown clearer groupings.
While functional groups have previously shown to be poor predictors of competitive interactions \parencite{bret2008plant}, studies in other contexts have succeeded in isolating functional groups by selecting for model parsimony \parencite{allesina2009food}.
In further support of functional groups over phylogeny, \textcite{uriarte2004spatially} found that grouping based light guilds (akin to functional groups; \cite{blondel2003guilds}) produced a parsimonious model more frequently than grouping taxonimically (with both groupings defined \emph{a priori}).
Perhaps an attempt to produce functional groups based upon competitive interactions is warranted, applying the framework I present here to a set of species spanning multiple functional groups.

Alternatively, it should be noted that the success of \textcite{allesina2009food} in isolating groups using AIC occurred in much larger study systems, with 25 or more species.
Alas, the algorithmic complexity of the brute force method I employed in this study is abyssmal, preventing the application of the method to studies with more than seven or eight species.
As such, a better method would be required to test for grouping of species interactions among a larger set of species.

In light of the failure to produce clear groups, perhaps the most curious aspect of the results is the disagreement between the likely coclassifications of species in the groupings of rows and of columns.
This is perhaps not surprising in hindsight, for there is no necessity that species respond to competition in the same manner that they cause it, especially in competition for certain resources such as space (the limiting resource presumed in these data) or light.
Yet the assumption that species should group equivalently in these two regards is frequently made, often implicitly and without comment \parencite[e.g.][]{martorell2014testing,ives2003estimating,gross2015stability}.
These results recommend more explicit questioning, and even testing, of that assumption when building future species interaction models.

All in all, the method of \emph{a posteriori} parsimony-based selection of groups has not proven to be greatly effective, at least on such a closely reated set of species.
However, the results suggest a number of pieces of advice which might be borne in mind whenever selecting groupings \emph{a priori} for use in species interaction models.
Firstly, there may be no single best grouping, but perhaps multiple rather distinct groupings which each perform similarly.
Secondly, phylogeny does not appear to provide appropriate groupings.
Lastly, one should not implicitly assume that species are grouped in the same way with regard to their effects upon other species and their response to them; distinct groupings of the two might well be considered.
